TacticToe: Learning the Game of Tactics

### 2018-02-19 tactictoe_jv.tex
minor

\begin{definition}\label{def:prod} (Productive tactic)
The application of a tactic on an open goal is called productive if and only if
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we
interrupt tactics after a short amount of time (0.05 seconds).
\item It does not loop, i.e its output does not contain any goals that appears 
in the ancestor of the node of the current goal.
\item It is not a parallel step, i.e its output is not a superset
of a list of goals produced from the same goal.
\end{itemize}

>>>>

\begin{definition}\label{def:prod} (Productive tactic)
The application of a tactic on an open goal is called productive if and only if
all the following conditions are satisfied:
\begin{itemize}
\item It does not fail or timeout. To prevent tactics from looping, we
interrupt tactics after a short amount of time (0.05 seconds).
\item It does not loop, i.e. its output does not contain any goals that appears 
in the ancestor of the node of the current goal.
\item It is not a parallel step, i.e. its output is not a superset
of a list of goals produced from the same goal.
\end{itemize}
